Numerical modelling of the Cordilleran ice sheet

### 2014-08-24 kappa.tex
Change to Nimbus Roman fonts.
Non-break space after (a), (b), (c), etc.

@@

\begin{figure*}[b]
  \subgraphics{a}{photo-glacier-crevasses}%
  \hspace{1cm}%
  \subgraphics{b}{photo-glacier-susitna}%
  \hspace{1cm}%
  \subgraphics{c}{photo-glacier-fold}%
  \caption{Illustration of various glacier ice behaviours:
           \textbf{(a)} surface crevasses formed by ice flow over a hidden
           bedrock knob, Glacier Blanc, French Alps, 2004;
           \textbf{(b)} medial moraines illustrating downhill ice flow on
           Susitna Glacier, Alaska Range, photo by Austin Post, 1970
           \citep{NSIDC.2009}; and
           \textbf{(c)} mountain glacier calving into a small lake, revealing a
           folded structure formed by deformed debris layers in the ice,
           Glacier d'Arsine, French Alps, 2004.}
  \label{fig:glacier-mechanics}
\end{figure*}

\begin{figure*}[b]
  \subgraphics{a}{photo-glacial-valley}%
  \hspace{1cm}%
  \subgraphics{b}{photo-erratic-boulder}%
  \hspace{1cm}%
  \subgraphics{c}{photo-melt-channels}%
  \caption{Different indicators of past glaciation:
           \textbf{(a)} glacial valley, exhibiting a broad, U-shaped profile
           characteristic of erosion by glaciers,
           Cirque du Fer-\`{a}-Cheval, French Alps, 2013;
           \textbf{(b)} erratic boulders, deposited in an improbable
           configuration as the glacier melted underneath,
           Finse area, Norwegian Scandes, 2011; and
           \textbf{(c)} lateral meltwater channels, formed on a gentle slope
           as the ice margin retreated towards the valley bottom, Tuya Lake
           area, Canadian Cordillera, 2012.}
  \label{fig:glaciation-indicators}
\end{figure*}

@@

\begin{figure}
  \includegraphics{paleo-timeseries}
  \caption{Palaeo-climate records of the last 800\,ka.
           \textbf{(a)} Benthic oxygen isotope (\chem{\delta^{18}O}) record
           from a compilation of globally-distributed deep sea sediment cores
           \citep{Lisiecki.Raymo.2005}. Higher \chem{\delta^{18}O} values
           correspond to periods of lower temperatures \citep{Emiliani.1955}
           or lower global sea level, and thus higher ice volume stored in
           glaciers and ice sheets on land \citep{Shackleton.1967}.
           \textbf{(b)} Temperature anomalies ($\Delta T$) reconstructed from a
           central Antarctic ice core \citep[EPICA Dome~C,][]{Jouzel.etal.2007}.
           The grey bands indicate the approximate time span of the last
           glacial period of 110 to 10\,ka.}
  \label{fig:paleo-timeseries}
\end{figure}

@@

\begin{figure}
  \includegraphics{paleo-glaciation}
  \caption{Spatial extent of ice sheet and glacier cover in the northern
           hemisphere \textbf{(a)} at present \citep{Patterson.Kelso.2014}, and
           \textbf{(b)} during the last glacial maximum
           \citep{Ehlers.Gibbard.2007}.}
  \label{fig:paleo-glaciation}
\end{figure}

@@

\begin{figure*}
  \subgraphics{a}{photo-vancouver-island}%
  \hspace{1cm}%
  \subgraphics{b}{photo-fraser-valley}%
  \caption{Contrasted climates of the North American Cordillera:
           \textbf{(a)} Pacific Coast at Vancouver Island, western British
           Columbia, by Martin Margold, 2010.
           \textbf{(b)} Fraser Valley, south-central British Columbia, 2010.}
  \label{fig:photo-fraser-valley}
\end{figure*}

@@

\begin{figure*}
  \includegraphics{plot-sdeffect}
  \caption{Effect of temperature variability on Cordilleran ice sheet
           simulations. Modelled basal topography and surface topography
           (250\,m contours). The simulations use atmospheric forcing from the
           NARR \citep{Mesinger.etal.2006}, a temperature depression of
           7\,\degC, and different treatments of temperature variability
           including
           \textbf{(a)} no daily variability, $\sPDD=0$;
           \textbf{(b)} a constant, mean summer (JJA), model domain-averaged
           standard deviation value, $\sPDD=3.09$\,K;
           \textbf{(c)} monthly standard deviation grids derived from the NARR
           and
           \textbf{(d)} monthly grids for ice-free terrain and the
           Greenland ice sheet, ERA-40-based \citep{Uppala.etal.2005}
           parametrisation in \PSDP, ${\sPDD=-0.15\cdot{T_m}+1.66}$.
           Differences in surface elevation are displayed relative to case (c).
           Note the different colour scales.}
  \label{fig:plot-sdeffect}
\end{figure*}

@@

\begin{figure*}
  \includegraphics{plot-snapshots}
  \caption{\textbf{(a)} Modelled growth and decay of the last Cordilleran ice
           sheet. Basal topography, surface topography (1\,km contours) and
           surface velocity (m/a) are model results.
           \textbf{(b)} Evolution of total ice volume during the last glacial
           cycle, expressed as metres of sea-level equivalent (m~s.l.e.). The
           simulation is performed on a 6\,km horizontal grid and adopts
           atmospheric fields from the NARR \citep{Mesinger.etal.2006} and
           temperature offset time-series derived from the GRIP ice-core record
           \citep{Dansgaard.etal.1993} as described in \CCYC. Note that, for
           this run, the Cordilleran ice sheet was almost as voluminous during
           MIS~4 as it was during the LGM.}
  \label{fig:plot-snapshots}
\end{figure*}

>>>>

% Nimbus fonts
\usepackage{times}
\urlstyle{same}

@@

\begin{figure*}[b]
  \subgraphics{a}{photo-glacier-crevasses}%
  \hspace{1cm}%
  \subgraphics{b}{photo-glacier-susitna}%
  \hspace{1cm}%
  \subgraphics{c}{photo-glacier-fold}%
  \caption{Illustration of various glacier ice behaviours:
           \textbf{(a)}~surface crevasses formed by ice flow over a hidden
           bedrock knob, Glacier Blanc, French Alps, 2004;
           \textbf{(b)}~medial moraines illustrating downhill ice flow on
           Susitna Glacier, Alaska Range, photo by Austin Post, 1970
           \citep{NSIDC.2009}; and
           \textbf{(c)}~mountain glacier calving into a small lake, revealing a
           folded structure formed by deformed debris layers in the ice,
           Glacier d'Arsine, French Alps, 2004.}
  \label{fig:glacier-mechanics}
\end{figure*}

\begin{figure*}[b]
  \subgraphics{a}{photo-glacial-valley}%
  \hspace{1cm}%
  \subgraphics{b}{photo-erratic-boulder}%
  \hspace{1cm}%
  \subgraphics{c}{photo-melt-channels}%
  \caption{Different indicators of past glaciation:
           \textbf{(a)}~glacial valley, exhibiting a broad, U-shaped profile
           characteristic of erosion by glaciers,
           Cirque du Fer-\`{a}-Cheval, French Alps, 2013;
           \textbf{(b)}~erratic boulders, deposited in an improbable
           configuration as the glacier melted underneath,
           Finse area, Norwegian Scandes, 2011; and
           \textbf{(c)}~lateral meltwater channels, formed on a gentle slope
           as the ice margin retreated towards the valley bottom, Tuya Lake
           area, Canadian Cordillera, 2012.}
  \label{fig:glaciation-indicators}
\end{figure*}

@@

\begin{figure}
  \includegraphics{paleo-timeseries}
  \caption{Palaeo-climate records of the last 800\,ka.
           \textbf{(a)}~Benthic oxygen isotope (\chem{\delta^{18}O}) record
           from a compilation of globally-distributed deep sea sediment cores
           \citep{Lisiecki.Raymo.2005}. Higher \chem{\delta^{18}O} values
           correspond to periods of lower temperatures \citep{Emiliani.1955}
           or lower global sea level, and thus higher ice volume stored in
           glaciers and ice sheets on land \citep{Shackleton.1967}.
           \textbf{(b)}~Temperature anomalies ($\Delta T$) reconstructed from a
           central Antarctic ice core \citep[EPICA Dome~C,][]{Jouzel.etal.2007}.
           The grey bands indicate the approximate time span of the last
           glacial period of 110 to 10\,ka.}
  \label{fig:paleo-timeseries}
\end{figure}

@@

\begin{figure}
  \includegraphics{paleo-glaciation}
  \caption{Spatial extent of ice sheet and glacier cover in the northern
           hemisphere \textbf{(a)}~at present \citep{Patterson.Kelso.2014}, and
           \textbf{(b)}~during the last glacial maximum
           \citep{Ehlers.Gibbard.2007}.}
  \label{fig:paleo-glaciation}
\end{figure}

@@

\begin{figure*}
  \subgraphics{a}{photo-vancouver-island}%
  \hspace{1cm}%
  \subgraphics{b}{photo-fraser-valley}%
  \caption{Contrasted climates of the North American Cordillera:
           \textbf{(a)}~Pacific Coast at Vancouver Island, western British
           Columbia, by Martin Margold, 2010.
           \textbf{(b)}~Fraser Valley, south-central British Columbia, 2010.}
  \label{fig:photo-fraser-valley}
\end{figure*}

@@

\begin{figure*}
  \includegraphics{plot-sdeffect}
  \caption{Effect of temperature variability on Cordilleran ice sheet
           simulations. Modelled basal topography and surface topography
           (250\,m contours). The simulations use atmospheric forcing from the
           NARR \citep{Mesinger.etal.2006}, a temperature depression of
           7\,\degC, and different treatments of temperature variability
           including
           \textbf{(a)}~no daily variability, $\sPDD=0$;
           \textbf{(b)}~a constant, mean summer (JJA), model domain-averaged
           standard deviation value, $\sPDD=3.09$\,K;
           \textbf{(c)}~monthly standard deviation grids derived from the NARR
           and
           \textbf{(d)}~monthly grids for ice-free terrain and the
           Greenland ice sheet, ERA-40-based \citep{Uppala.etal.2005}
           parametrisation in \PSDP, ${\sPDD=-0.15\cdot{T_m}+1.66}$.
           Differences in surface elevation are displayed relative to case (c).
           Note the different colour scales.}
  \label{fig:plot-sdeffect}
\end{figure*}

@@

\begin{figure*}
  \includegraphics{plot-snapshots}
  \caption{\textbf{(a)}~Modelled growth and decay of the last Cordilleran ice
           sheet. Basal topography, surface topography (1\,km contours) and
           surface velocity (m/a) are model results.
           \textbf{(b)}~Evolution of total ice volume during the last glacial
           cycle, expressed as metres of sea-level equivalent (m~s.l.e.). The
           simulation is performed on a 6\,km horizontal grid and adopts
           atmospheric fields from the NARR \citep{Mesinger.etal.2006} and
           temperature offset time-series derived from the GRIP ice-core record
           \citep{Dansgaard.etal.1993} as described in \CCYC. Note that, for
           this run, the Cordilleran ice sheet was almost as voluminous during
           MIS~4 as it was during the LGM.}
  \label{fig:plot-snapshots}
\end{figure*}
